\texttt{Anon}Dataset: A collection of benchmark datasets for learning with graphs

### 2020-06-08 main.tex
CM

\begin{abstract}
Recently, there has been an increasing interest in (supervised) learning with graph data, especially using graph neural networks.  However, the development of meaningful benchmark datasets and standardized evaluation procedures is lagging. That is, most papers still evaluate their methods on small-scale datasets leading to high standard deviations and hard to interpret results, consequently hindering advancements in this area. To address this, we introduce the \textsc{\texttt{Anon}} for graph classification and regression. The dataset consists of over 120 datasets from a wide range of applications and varying sizes. We provide Python-based data loaders, kernel, and graph neural network baseline methods implementations, and evaluation tools. Here, we give an overview of the datasets, standardized evaluation procedures, and provide baseline experiments. All datasets are available at \url{Anon}. The experiments are fully reproducible from the code available at \url{www.github.com/Anon}.
\end{abstract}

@@

\xhdr{Present work.} 
Here, we give an overview of \textsc{\texttt{Anon}}. The benchmark collection consists of over 120 datasets from a wide range of domains for supervised learning with graphs, i.e., classification and regression. All datasets are provided in a standard dataset format at \url{Anon} and are easily accessible from popular graph learning frameworks such as \textsc{Pytorch Geometric}~\cite{Fey+2019} and \textsc{DGL}~\cite{Wan+2019}. To facilitate standard comparison of kernel and neural approaches, we provide implementations of standard algorithms and easy-to-use evaluation procedures. Moreover, we report results on an experimental study comparing graph kernels and GNNs on a subset of the \textsc{\texttt{Anon}}.

@@

The papers~\cite{Fey+2019,Che+2019new,Err+2019,Dwi+2020} evaluate GNNs using a unified evaluation procedure, however, they only use small- or medium scale datasets. Recently, \url{ogb.stanford.edu}~\cite{Hu+2020} launched, however, the provided datasets for graph classification focus on chemistry and bioinformatic applications, and the number is quite limited at this point. Moreover, the datasets proposed in~\cite{Fer+2019} focuses on instances from planning competitions. http://www.jmlr.org/papers/volume21/18-370/18-370.pdf

@@

The \texttt{Anon} contains over 120 datasets provided at \texttt{Anon}. The data baseline methods and experimental evaluation tools can be installed by running \texttt{pip install Anon}. See the website for dataset statistics and documentation.

>>>>

\begin{abstract}
Recently, there has been an increasing interest in (supervised) learning with graph data, especially using graph neural networks.  However, the development of meaningful benchmark datasets and standardized evaluation procedures is lagging. That is, most papers still evaluate their methods on small-scale datasets leading to high standard deviations and hard to interpret results, consequently hindering advancements in this area. To address this, we introduce the \textsc{\texttt{Anon}} for graph classification and regression. The dataset consists of over 120 datasets from a wide range of applications and varying sizes. We provide Python-based data loaders, kernel, and graph neural network baseline methods implementations, and evaluation tools. Here, we give an overview of the datasets, standardized evaluation procedures, and provide baseline experiments. All datasets are available at \url{www.anon.io}. The experiments are fully reproducible from the code available at \url{www.github.com/Anon}.
\end{abstract}

@@

\xhdr{Present work.} 
Here, we give an overview of \textsc{\texttt{Anon}}. The benchmark collection consists of over 120 datasets from a wide range of domains for supervised learning with graphs, i.e., classification and regression. All datasets are provided in a standard dataset format at \url{www.Anon.io} and are easily accessible from popular graph learning frameworks such as \textsc{Pytorch Geometric}~\cite{Fey+2019} and \textsc{DGL}~\cite{Wan+2019}. To facilitate standard comparison of kernel and neural approaches, we provide implementations of standard algorithms and easy-to-use evaluation procedures. Moreover, we report results on an experimental study comparing graph kernels and GNNs on a subset of the \textsc{\texttt{Anon}}.

@@

The papers~\cite{Fey+2019,Che+2019new,Err+2019,Dwi+2020} evaluate GNNs using a unified evaluation procedure, however, they only use small- or medium scale datasets. Recently, \url{ogb.stanford.edu}~\cite{Hu+2020} launched, however, the provided datasets for graph classification focus on chemistry and bioinformatic applications, and the number is quite limited at this point. Moreover, the datasets proposed in~\cite{Fer+2019} focuses on instances from planning competitions. Moreover, the \textsc{GraKeL} library~\cite{Sig+2018} provides an implemention of common graph kernels.

@@

The \texttt{Anon} contains over 120 datasets provided at \texttt{www.anon.io}. The data baseline methods and experimental evaluation tools can be installed by running \texttt{pip install Anon}. See the website for dataset statistics and documentation.
